The semantic drift of quotations in blogspace: a case study in short-term cultural evolution

### 2016-08-23 reviews/2016-07-response-to-reviewers.tex

\medskip
We look forward to reading your feedback on this new manuscript and apologize in advance for this long revision round.

\bigskip
Best wishes,

\bigskip
Sébastien Lerique and Camille Roth

\subsection*{Editor}
\critique{
1. The main results of the paper are based on a lot of arbitrary decisions about how various quantities are defined.  I am interested if small differences in these choices radically changes the conclusions you would draw, and how many other approaches you tried before you arrived at the data patterns you present.  All the reviewers agreed on this point (asking for more clarification about feature selection, why certain choices were made in the analysis, etc…).  This ranges from what types of quotes were included, to the rules for detecting substitution errors, to the inclusion of certain features in your analyses.  The reader needs to be convinced that the few “strong” looking patterns you do find are not too dependent on these arbitrary choices.  I actually question if this is the best way to address this question (effect of memory and linguistic variables on copy errors) given the noisiness of the data and the difficulty in attributing copying errors to any particular parent
source.

@@

}

\answerok{
We acknowledge these issues and worked extensively to address them.  In particular (further details may also be found in the responses to reviewers): 
\itx{
\x We developed a variety of substitution models to show that the results are robust
\x We rationalized feature selection, adding some variables and much detail to this section
\x In general, we clarified further the assumptions and decisions made, such as the restriction to single substitutions
\x We also introduced manually-coded precision \& recall analyses for all filters, justifying relevant choices.
}
}

@@

\answerok{We agree that the initial manuscript overstated some results. We believe the new manuscript states its claims more appropriately, and makes a better distinction between actual conclusions and open questions that could not be addressed given the data (in particular, we attempted to explore substitution chains in earlier stages of this work, but were quickly limited by the constraints of the data).

We had also overlooked several developments in the iterated learning literature, and are grateful for the various pointers. The works we thought were most relevant have been integrated to the introductory sections, and their implications for our work are discussed in the new ``Discussion'' section.
}

\critique{3. The writing of this paper is of very low quality compared to what is expected at the journal.  I will email separately a very detailed editing of the paper via Adobe Acrobat where I tried to point these problems out.  However, it simply couldn’t be published without a nearly complete re-write or very heavy editing.
}

\answerok{Thank you for this very constructive and extensive feedback. We paid significant attention to the writing style in this new version, and large portions of the document have been rewritten and expanded --- all updates are marked in dark blue.}

@@

%\critique{
%The bottom line is that while I think this is a really interesting idea/question, this is not the best execution of this idea that I could imagine being published in the journal.  My gut reaction is that this paper needs a lot of work, additional analysis, and rewriting before it could be published and therefore should be rejected.  However, because the reviewers are unanimously more positive in their evaluation I will invited a revision for this in the hope that you can make it a pretty significant change and can benefit from the excellent and detailed reviewer comments.
%
%So you understand what is requested:  typically papers which are revised at Cognitive Science are returned with a detailed cover letter responding to each of the reviewer comments in detail, along with pointers to what has changed in the paper.  I would appreciate this type of cover letter if you choose to resubmit because it can help me and the reviewers process what changes you made.
%
%Sincerely,
%Todd Gureckis
%Associate editor
%}
%
%\answer{
%}

\subsection*{Reviewer \#1}

\critique{I think this is an interesting approach and dataset for better understanding how sentences are recalled and how paraphrases are constructed.  However, I think that the experiment design needs to be refined, and the project as a whole needs to be better connected to larger theoretical problems and better grounded within cognitive science.}

\answerok{We have been careful to introduce many more connections to the relevant works in cognitive science: the introduction has been entirely rewritten and is followed by a more thorough presentation of the related work, while the concluding sections (discussion \& concluding remarks) follow your recommendation of connecting our results with the literature.
}

@@

\answerok{We thoroughly reworked the general grounding and flow of the manuscript. In particular:
\itx{
\x We believe that the introductory parts provide a clearer presentation of our question and how it relates to existing literature (including the areas we overlooked) and hypotheses
\x The new ``Discussion'' section, which was indeed missing, should properly reconnect our results to the related works introduced at the beginning of the paper.
}

Finally, several modifications in the ``Results'' section (more examples, a short discussion of the distance traveled by substitutions on the synonym network in footnote \#15, and the addition of the second null hypothesis $\mathcal{H}_{00}$ in the ``Variation'' subsection) should better describe the type of changes undergone by quotes.
}

\critique{The experiment design also has some substantial flaws. First, some crucial factors were not considered - most notably, part of speech. I suspect, for instance, that pronouns and other closed-class words are less often substituted than open-class words.  Phonological neighborhood density could also be important, though probably less so.  Second, no analysis was done that included all of the factors in, e.g., a multi-feature regression model.  While the features being considered are not strongly correlated, they are still likely to interact - especially if part-of-speech is added.  Third, the restriction to single-word substitutions introduces some significant confounds.  I'm not convinced that correctly and incorrectly copying a quote should be viewed as separate behaviors.
}

\answerok{
We addressed these points in the revised version:
\itx{
\x We checked and discussed the susceptibility of part-of-speech (POS). While \tb{a rigorous treatment of} the open-/closed-class question is largely precluded by our exclusion of stopwords from the analysis (which led us to not discuss that point in the manuscript), \tb{the data does indeed indicate that closed class words are less substituted than open class words (the \emph{Closed class-like} category is mainly made of \tb{closed class words})}. As the manuscript discusses however, this concerns less than 7\% of the substitutions we consider, and has likely no effect on our results.
\x Following this suggestion, we added phonological neighborhood density as a word feature. We show that it forms a subgroup of strongly correlated variables, together with orthographic neighborhood density, and choose the latter as a more natural representative of this subgroup given the task studied.
\x We introduced a multi-feature regression model to estimate variation upon substitution, showing that the magnitude of the variation of a feature is mainly predicted by the {start word's value for} that very feature, generally with negligible interaction with the other features (see also below and figure 8).
\x We expanded substitution models to {also detect quotes undergoing up to two substitutions}, which yielded the same results as single substitutions {(see below)}. 
}

@@

\answerok{The case presented here is valid and could indeed hide a bias in our measures.
Rather than analyzing all possible such cases to bound the error, we extended substitution models to detect quotes undergoing up to two substitutions, and applied the same analysis to these mined substitutions. The results were unchanged (note: graphs produced for all models may be found at <https://huit.re/aEH77Gc3>, and may be commented further upon request). For example, the extended version of the model presented in the paper mines 70k substitutions, 9.2k of which are kept after filtering (the lowered acceptance rate indicates that more invalid substitutions are generated when allowing up to two substitutions per quote).

We did not expand to more than two substitutions, as more than 20\% of quotes are 5 to 9 words long (with a minimum of 5 words for quotes in the data set). For such quotes, three or more substitutions means changing at least a third of the sentence, which makes any attempt to link it to a similar variant pointless.
}

\critique{ Some high-level suggestions:
\itx{
\x more discussion of what dynamical systems are and especially their interpretation in this task before their appearance in the results}
}

\answerok{The rewritten ``Variation'' subsection (including footnote \#21) should now clarify this notion.}

@@

\critique{\itx{
\x improving statements of motivation and grounding within cognitive science
\x what are representation transformation processes?
\x give examples in the introduction
\x show how the quotation test case connects to more general representation transformation?}
}

\answerok{
These points should be addressed by the improved introduction. In particular regarding the last question, the new ``Discussion'' section additionally makes a connection with the iterated learning literature.
}

\critique{\itx{
\x what about the semantics of quote replication?
\x does part of speech influence substitution rate?
\x can you quantify the semantic distance between the original and substituted quote (e.g., get Mechanical Turkers to rate the semantic distance?)}
}

\answerok{We added a short discussion on the semantics of substituted quotes. We first aimed at quantifying the semantic distance by estimating the distance ``traveled'' by the substituted word in the WordNet hypernym-hyponym network as well as the FA network. This showed that substituted and substituting words are rarely direct synonyms, yet they usually achieve a similar meaning in the context of their sentence.
To further grasp the relationship of substitutions to synonyms we introduced a second null hypothesis in the ``Variation'' subsection, which compares the actual variation to what would happen if a random synonym of the start word were picked instead.

@@

Finally, we also examined the effect of part-of-speech (POS): Fig. 5 details the results on five POS categories, \tb{with a discussion of the corresponding effects in the main text, explaining} why we largely keep POS outside of our analysis.
}

\critique{\itx{
\x what happens when you run a multi-factor regression model? Do the features interact?
}}

\answerok{We introduced a simple regression model to check for feature interactions, which is presented in Fig. 8 with a corresponding discussion (in a nutshell: we show that features generally do not interact).}

@@

\critique{Some low-level points:\itx{
\x the in vitro/in vivo distinction is unfamiliar and ought to be defined in the text
}
}

\answerok{In light of this potential unfamiliarity, we preferred to entirely avoid referring explicitly to this dichotomy (for instance, we now speak of ``corpus-based utterances'' instead of ``in vivo'').}

\critique{\itx{
\x introducing eight measures and then removing three of them due to collinearity is presentationally confusing}}

\answerok{We agree that introducing twelve\footnote{In the revised version we have 12 measures, instead of 8 in the initial submission.} measures before eventually keeping six of them could complicate the flow of the section on word-level measures. However, we found it more natural to first propose a comprehensive list of candidate features based on the literature before addressing the quantitative analysis with a reduced yet sufficient set of metrics --- especially now that this section has been significantly expanded. We initially favored this solution over first presenting the final list of candidate features and justifying afterwards that they are anyway correlated with a broader list of traditional variables. (Note: an alternative option could consist in presenting the contents of Figs. 1 and 2 in the same figure, if this would be less confusing.)}

@@

\critique{
\itx
{
\x was there a reason to expect that \# of synonyms and \# of phonemes would interact (Fig. 4)?]
}
}

\answerok{Except for word frequency, we observed that synonyms and phonemes were the only two word features to exhibit an effect on susceptibility (and a quite similar effect for that matter). We thus reasoned that they might exhibit a joint effect.

However, the revised version now features a broader analysis assessing joint effects (see Fig. 8); we think it favorably replaces the previous variable-to-variable correlation check. (Note: we also replaced number of phonemes with number of letters, which makes more sense in our context -- see the end of the ``Word-level measures'' subsection. The latter does not seem to interact with number of synonyms.)}

@@

Notwithstanding, data in the new Figs. 6, 7, 9 \& 10 is now binned into 4 quartile-based bins, which makes more sense for the confidence intervals. This decision was reached after exploring several other binning configurations: none of these substantially changed the results, but opting for quartile-based bins does improve the overall readability. Notably, no multiple crossovers were ever observed.
}

\subsection*{Reviewer \#2}
\critique{This is a review of "How do we copy and paste? The semantic drift of quotations in blogspace." This paper attempts to discover the underlying psycholinguistic variables that is involved in blog authors making mistakes in the copying of quotations across time. Although I think the motivations and goals of this article are interesting and noteworthy, I think the actual analysis needs improvement in a number of areas.

Although I appreciate the brief writeup on intrusions in recall, the article fails to capture the amount of research done on this topic. Going back to Deese (1959; the precursor to modern experimental studies on false memory) and the subjective organization results of Tulving (1962) it has been well known that extra-list intrusions in free recall are often semantic in nature, with the intruding word being very similar in meaning to a studied item. A recent study that reinforces this is one by Zaromb, et al. (2006; JEP:LMC).
}

\answerok{Thank you for these very useful and, indeed, relevant pointers.  We accordingly devoted a significant portion of the literature review to the issue of recall (see the ``Related work'' and ``Discussion'' sections).}

@@

I would guess that the substitutions that are made in quotations are overwhelmingly higher frequency, highly semantically similar words. As the example on pg. 19 states, the substitution was "world" for "globe," where a higher frequency word replaced a lower frequency, semantically related word. There are a number of different models that can be used to assess this type of similarity, with the classic model being latent semantic analysis (Landauer \& Dumais, 1997). There are a number of additional models that have been proposed, such as Topics (Griffiths, Steyvers, \& Tenenbaum, 2007, Psyc Review) or Beagle (Jones \& Mewhort, 2007, Psyc Review). These models differ in their implementational complexity, but there are tools available that allow for useful statistics to be acquired easily. A tool by Recchia \& Jones (2010, BRM) allows for pointwise mutual information (PMI) of different words to be retrieved from a given corpus very simply. A tool such as this would allow for word-word similarity to be included in the analysis.

I understand that word-word metrics are not easily introduced in the type of analysis that the authors are attempting to do, where the analysis of the contributions of different global psycholinguistic variables are being weighed against each other. I just think that type of analysis is inappropriate here. Since the quotations were selected on the basis of single substitutions, it seems to me that the appropriate level of analysis is what properties of the word that is being substituted is the most predictive of the substitution. I suspect that the combination of frequency and semantic similarity will be by far the most predictive variables, consistent with past results on recall.
}

\answerok{The rewritten introductory sections of this revision now aim at explaining why we chose to use a feature-based analysis over the prediction of individual words (see below for more details about this).
Word-word similarity is now also shortly discussed in the beginning of the ``Results'' section (and in footnote \#15). We explored a number of other similarity measures provided by WordNet (based on paths in the WordNet network, or on similarity of Information Content extracted from external corpora), but none of them provided more insight than what is being discussed in that section.

@@

\critique{ A second issue is the time spent on feature selection.  It is unclear why the authors do feature selection at all, as "the analysis is done on a per-feature basis."  It would again add to the robustness of their claims if they showed that all of the correlated features show the same pattern of susceptibility and bias in substitution.  In the same vein, it is not clear why the authors claim that age of acquisition, frequency, and number of synonyms have low levels of correlation "excluding the network properties".  Why would one ignore the correlations with the network features?
}

\answerok{Our feature selection step aims at making the results more intelligible. This section was indeed poorly written, and has been thoroughly revised to rationalize the process. In particular, we identify (six) groups of strongly correlated features (both manually by visual inspection and automatically with the help of an agglomeration algorithm, yielding identical results) and justify the choice of our six prototype features for each group.  Features belonging to the same group generally exhibit very similar behaviors across all measures (with few exceptions, notably number of phonemes and number of syllables \tb{exhibiting less cognitive bias} than number of letters). Graphs produced for all features may be found at <https://huit.re/aEH77Gc3>, and could be included in a Supplementary Information bundle if requested.
}

\critique{
One smaller issue has to do with the filtering of the quotations.  The authors manually inspected the filtered quotes to see how many real event-related utterances are incorrectly filtered, but I would argue the precision of the filter is more important than the recall; how many of the kept quotes are not real event-related utterances?  Why not do manual coding of those and report that accuracy?
}

\answerok{This is an important empirical point which we did not address systematically in the first submission.  We have now done this manual coding step, and have improved filters wherever precision or recall (whichever was most relevant) were not good enough. We now assess filtering accuracy systematically and it is satisfying in the relevant cases.}

### 2016-08-23 brains-conclusion.tex
Editorial changes after full proof-read (after a long rest)

We initially aimed to connect the field of cultural evolution with psycholinguistics by asking if cultural attractors appear in a corpus of online news-related quotes which are gradually transformed by low-level biases.
The data set we used imposed a few constraints on our analysis:
first, it was necessary to infer source-destination links, an operation made more reliable when restricting the scope of transformations to very simple cases, which we did by focusing on word substitutions.
Second, contrary to laboratory experiments which produce data made of many repeated measures on a small number of cases (\hbox{e.g.} a given list of words), we have a great number of different cases (one case per cluster in which substitutions are found, \hbox{i.e.} 698 cases), with very few measures on each of them (average 9, median 5).
This rendered the prediction of individual words impractical: if we cannot compute a percentage of explained data for a given case, any approximate prediction will be heavily underestimated.
This last factor, added to the potential for variation of external conditions when authors wrote the quotes, led us to use word features to analyze the transformations by aggregating over individual cases.

By characterizing substitutions with 6 features on the disappearing word, we show that authors preferentially substitute words known for being harder to recall:
most prominently words with low frequency~\citep{gregg_word_1976}, learned later~\citep{dewhurst_separate_1998}, or made up of more letters~\citep{nickels_dissociating_2004}, both globally and in comparison to the sentence they appear in.
Further characterizing the substitutions by examining the variation of word features from disappearing to appearing words, we show:
(1) that the operation is contractile on average, that is words are brought closer to an attractor point on each feature;
(2) that authors produce words that are easier to remember than the average of synonyms of the disappearing word (a fact that is reflected in the position of the attraction point).

We do not actually observe quotes converging on a global scale towards attractors in their various dimensions.
Indeed the limits of the data set do not allow us to infer chains of substitutions, and substitutions themselves are not the only type of transformation at work in the data set.
Nonetheless, these findings (1) bring light to this simple type of transformation, and (2) are consistent with known psycholinguistic effects, with the hypothesis of cultural attractors in representations from everyday life, and with the lineage specificity discussed in the iterated learning literature~\citep{claidiere_cultural_2014,cornish_systems_2013}.
They are obtained by successfully applying knowledge from cognitive science to real-life complex data, a task that remains a challenge in the study of cultural evolution.
More broadly, we believe that applying such data mining tools to manage the complexity of real-life data is a promising approach for the joint analysis of cognitive science and culture.

@@

\newtext{The theory of Epidemiology of Representations proposes a unifying framework for the study of cultural evolution.
One of its core claims, the existence of cultural attractors, has been both a challenge to test empirically and a fruitful line to pursue in the study of cultural evolution.}
We aimed to contribute to \newtext{testing this hypothesis} by studying a simple everyday-life task where individuals are implicitly trying to reproduce quotations.
To some extent, our work amounts to \newtext{an out-of-laboratory} experiment where we \newtext{examine the influence} of \newtext{well-known word features} on the accuracy of the reproduction of short sentences.
\newtext{Our analysis of substitutions shows that words are attracted, in each dimension, to feature-specific values.
Furthermore, the features' known effects in psycholinguistic experiments are reflected in the biases of these attraction points, meaning that the evolution of such quotations can be partially explained by known low-level cognitive biases.
We believe that such an approach, combining psycholinguistic knowledge and data mining tools, can be fruitfully developed to improve the study of cultural attractors and explore the reciprocal influences of cognition and culture.}

@@

Let us conclude by noting that the question of short- and long-term cultural evolution, and the approaches to study them, are becoming increasingly relevant to other fields.
In biology in particular, work on evo-devo and non-genetic inheritance has accumulated evidence that is poorly accounted for by the modern synthesis of biological evolution, and is creating a demand for new or extended  approaches to joint cultural and biological evolution~\citep[see][for instance]{gilbert_eco-evo-devo:_2015}.
Such an approach has long been called upon by anthropologists like~\citet{ingold_beyond_2004,ingold_three_1999}, in line with Mauss' initial works~\citep{mauss_les_1936}, and the debate is not entirely foreign to the enactive-representational discussion in cognitive science.
%As regards our particular case, a most promising line of work on the evolution of language is being developed by \citet{cuffari_participatory_2014}.
The study of cultural evolution will most likely benefit greatly from the growing interactions between these disciplines.

>>>>

We initially aimed to connect the field of cultural evolution with psycholinguistics by asking if cultural attractors appear in a corpus of online news-related quotes gradually transformed by low-level biases.
The data set we used imposed a few constraints on our analysis:
first, it was necessary to infer source-destination links, an operation made more reliable when restricting the scope of transformations to very simple cases, which we did by focusing on single word substitutions.
Second, contrary to laboratory experiments which produce data made of many repeated measures on a small number of cases (\hbox{e.g.} a given list of words), we have a great number of different cases (one case per cluster in which substitutions are found, \hbox{i.e.} 698 cases), with very few measures on each of them (average 9, median 5).
This rendered the prediction of individual words impractical: if we cannot compute a percentage of explained data for a given case, any approximate prediction will be heavily underestimated.
This last factor, added to the potential for variation of external conditions when authors wrote the quotes, led us to use word features to analyze the transformations by aggregating over individual cases.

By characterizing substitutions with 6 features on the disappearing word, we show that authors preferentially substitute words known for being harder to recall:
most prominently words with low frequency~\citep{gregg_word_1976}, learned later~\citep{dewhurst_separate_1998}, or made up of more letters~\citep{nickels_dissociating_2004}, both globally and in comparison to the sentence they appear in.
Further characterizing the substitutions by examining the variation of word features from disappearing to appearing words, we show:
(a) that the operation is contractile on average, that is words are brought closer to an attractor point on each feature;
(b) that authors produce words that are easier to remember than the average of synonyms of the disappearing word (a fact that is reflected in the position of the attraction point).

We do not actually observe quotes converging on a global scale towards attractors in their various dimensions.
Indeed the limits of the data set do not allow us to infer chains of substitutions, and substitutions themselves are not the only type of transformation at work in the data set.
Nonetheless, these findings (a) bring light to this simple type of transformation, and (b) are consistent with known psycholinguistic effects, with the hypothesis of cultural attractors in representations from everyday life, and with the lineage specificity discussed in the iterated learning literature~\citep{claidiere_cultural_2014,cornish_systems_2013}.
They are obtained by successfully applying knowledge from cognitive science to real-life complex data, a task that remains a challenge in the study of cultural evolution.
More broadly, we believe that applying such data mining tools to manage the complexity of real-life data is a promising approach for the joint analysis of cognitive science and culture.

@@

\newtext{The theory of Epidemiology of Representations proposes a unifying framework for the study of cultural evolution.
One of its core claims, the existence of cultural attractors, has been both a challenge to test empirically and a fruitful line to pursue in the study of cultural evolution.}
We aimed to contribute to \newtext{testing this hypothesis} by studying a simple everyday-life task where individuals are implicitly trying to reproduce quotations.
To some extent, our work amounts to \newtext{an out-of-laboratory} experiment where we \newtext{examine the influence} of \newtext{well-known word features} on the accuracy of reproduction of short sentences.
\newtext{Our analysis of substitutions shows that words are attracted, in each dimension, to feature-specific values.
Furthermore, the features' known effects in psycholinguistic experiments are reflected in the biases of these attraction points, meaning that the evolution of such quotations can be partially explained by known low-level cognitive biases.
We believe that such an approach, which combines psycholinguistic knowledge and data mining tools, can be fruitfully developed to improve the study of cultural attractors and explore the reciprocal influences of cognition and culture.}

@@

Let us conclude by noting that the question of short- and long-term cultural evolution, and the approaches to study them, are becoming increasingly relevant to other fields.
In biology in particular, work on evo-devo and non-genetic inheritance has accumulated evidence that is poorly accounted for by the modern synthesis of biological evolution, and is creating a demand for new or extended  approaches to joint cultural and biological evolution~\citep[see][for instance]{gilbert_eco-evo-devo:_2015}.
Such an approach has long been called upon by anthropologists like~\citet{ingold_beyond_2004,ingold_three_1999}, in line with Mauss' initial works~\citep{mauss_les_1936}, and the question is not entirely foreign to the enactive-representational debate in cognitive science.
%As regards our particular case, a most promising line of work on the evolution of language is being developed by \citet{cuffari_participatory_2014}.
The study of cultural evolution will most likely benefit greatly from the growing interactions between these disciplines.

### 2016-08-23 brains-introduction.tex
Editorial changes after full proof-read (after a long rest)

The theory of epidemiology of representations proposes a unifying framework for all these works by recasting them as questions of spread and transformation of representations:
these are alternatively located in the mind (``mental representations'' in Sperber's terminology), or in the outer world (``public representations'') as expressions of mental representations in diverse cultural artifacts (pieces of text, utterances, pictures, building techniques, etc.).
A human society is then modeled as a large dynamical system of people constantly interpreting public representations into mental representations, and producing new public representations based on what they have previously interpreted.
Two key points are that (a) transmission is not reliable (representations change significantly each time they are interpreted and produced anew, as opposed to \hbox{e.g.} memetics), and (b) the reciprocal influences of cognition and culture can be captured by studying the evolution of public representations themselves, which is what the above-cited studies are doing.

@@

To show this we analyze how quotes in blogs and media outlets are modified when they are copied from website to website.
These public representations should normally not change as they spread on the Web (as opposed to more elaborate expressions or opinions, not identified as quoted utterances), but empirical observation shows that they are in fact occasionally transformed~\citep{simmons_memes_2011}:
authors spontaneously transform quotes, not only cropping them but also replacing words.
For instance the quote ``we will not be scared of these cowards'' (a substring of a quote from former Pakistani President Asif Ali Zardari) is also found as ``we will not be \textbf{afraid} of these cowards''.
More meaningful changes often happen too, such as the transformation of McCain's ``I admire Senator Obama and his accomplishments'' during the 2008 U.S. presidential campaign, into ``I \textbf{respect} Senator Obama and his accomplishments''.
Since authors are implicitly required to copy quotes exactly, we can assume that most transformations, especially simple ones such as those shown above, are the result of automatic (\hbox{i.e.} hard to control) low-level cognitive biases of the authors.

@@

Compared to full sentences, recall of word lists provides a situation that is easier to fully explore, and that has been extensively studied.
In particular, the Deese, Roediger, and McDermott paradigm (introduced by \citealp{deese_prediction_1959}, and later popularized by \citealp{roediger_creating_1995}) has shown that it is possible to construct lists of words which reliably create the false memory of an external word related to those in the list.
This is done by using lists of words produced by free association from the target intrusion word;
the intruding recall then happens with probability nearly proportional to the average semantic association strength between the intruding word and the words in the list.
A sizable literature studies this type of task with varying complexities in the design of the lists, a good review of which is given by \citet{zaromb_temporal_2006}.
One notable effect is that the semantic relations between words greatly influence, and correlate to, the order in which words are recalled~\citep{tulving_subjective_1962,howard_when_2002}, and that this reordering of items improves subjects' repeated recalls~\citep{tulving_subjective_1966}.
The frequency and type of intrusions in lists of random words are also influenced by associations created by the presentation of previous lists~\citep{zaromb_temporal_2006}.
Indeed, the question of how such temporal associations (contributing to contextual information retrieval in recall) interact with the prior semantic associations of subjects (contributing to associative information retrieval) is at the core of many of these studies.

@@

\newtext{Given this complexity we decided to focus on more aggregate effects, where variations of the conditions in which sentences are read and produced have a chance of being statistically smoothed out.\footnote{
\newtext{Aside from our lack of control on the precise conditions of encoding and recall in our data set, the analysis techniques mentioned above are better suited to data consisting of a high number of measures over a smaller number of lists (in which case it makes sense to ask \hbox{e.g.} what proportion of intrusions come from prior lists).
As is explained further down however, our data set is shaped the opposite way: a great number of sentences, with only very few to no measures at all on each sentence.
}}
If a cognitive bias in the substitution of words manifests itself with simple measures, then it} \newtext{will be worth applying predictive models of the substitution process in further research.}

>>>>

The theory of Epidemiology of Representations proposes a unifying framework for all these works by recasting them as questions of spread and transformation of representations:
these are alternatively located in the mind (``mental representations'' in Sperber's terminology), or in the outer world (``public representations'') as expressions of mental representations in diverse cultural artifacts (pieces of text, utterances, pictures, building techniques, etc.).
A human society is then modeled as a large dynamical system of people constantly interpreting public representations into mental representations, and producing new public representations based on what they have previously interpreted.
Two key points are that (a) transmission is not reliable (representations change significantly each time they are interpreted and produced anew, as opposed to \hbox{e.g.} memetics), and (b) the reciprocal influences of cognition and culture can be captured by studying the evolution of public representations themselves, which is what the above-cited studies are doing.

@@

To show this we analyze how quotes in blogs and media outlets are modified when they are copied from website to website.
These public representations should normally not change as they spread on the Web (as opposed to more elaborate expressions or opinions, not identified as quoted utterances), but empirical observation shows that they are in fact occasionally transformed~\citep{simmons_memes_2011}:
authors spontaneously transform quotes, not only cropping them but also replacing words.
For instance the quote ``we will not be scared of these cowards'' (a substring of a quote from former Pakistani President Asif Ali Zardari) is also found as ``we will not be \textbf{afraid} of these cowards''.
More meaningful changes often happen too, such as the transformation of McCain's ``I admire Senator Obama and his accomplishments'' during the 2008 US presidential campaign, into ``I \textbf{respect} Senator Obama and his accomplishments''.
Since authors are implicitly required to copy quotes exactly, we can assume that most transformations, especially simple ones such as those shown above, are the result of automatic (\hbox{i.e.} hard to control) low-level cognitive biases of the authors.

@@

Compared to full sentences, recall of word lists provides a situation that is easier to fully explore and has been extensively studied.
In particular, the Deese, Roediger, and McDermott paradigm (introduced by \citealp{deese_prediction_1959}, and later popularized by \citealp{roediger_creating_1995}) has shown that it is possible to construct lists of words which reliably create the false memory of an external word related to those in the list.
This is done by using lists of words produced by free association from the target intrusion word;
the intruding recall then happens with probability nearly proportional to the average semantic association strength between the intruding word and the words in the list.
A sizable literature studies this type of task with varying complexities in the design of the lists, a good review of which is given by \citet{zaromb_temporal_2006}.
One notable effect is that the semantic relations between words greatly influence, and correlate to, the order in which words are recalled~\citep{tulving_subjective_1962,howard_when_2002}, and that this reordering of items improves subjects' repeated recalls~\citep{tulving_subjective_1966}.
The frequency and type of intrusions in lists of random words are also influenced by associations created by the presentation of previous lists~\citep{zaromb_temporal_2006}.
Indeed, the question of how such temporal associations (contributing to contextual information retrieval in recall) interact with the prior semantic associations of subjects (contributing to associative information retrieval) is at the core of many of these studies.

@@

\newtext{Given this complexity we decided to focus on more aggregate measures, where variations of the conditions in which sentences are read and produced have a chance of being statistically smoothed out.\footnote{
\newtext{Aside from our lack of control on the precise conditions of encoding and recall in our data set, the analysis techniques mentioned above are better suited to data consisting of a high number of measures over a smaller number of lists (in which case it makes sense to ask \hbox{e.g.} what proportion of intrusions come from prior lists).
As is explained further down however, our data set is shaped the opposite way: a great number of sentences, with only very few to no measures at all on each sentence.
}}
If a cognitive bias in the substitution of words manifests itself with simple measures, then it} \newtext{will be worth applying predictive models of the substitution process in further research.}
